\documentclass[a4paper,10pt]{article}
\usepackage[left=0.4in,right=0.4in,top=0.3in,bottom=0.3in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*, noitemsep, before=\small}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontspec}
% Remove page numbers
\pagestyle{empty}
% Section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{2pt}
% Custom commands
\newcommand{\entry}[4]{
  \noindent\textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4}
}
\begin{document}
% Header
\begin{center}
    {\Huge \textbf{JERRY (CHIEN-JUI) CHEN}} \\
    Irvine, CA | +1 682 390 9456 | \href{mailto:jhinresh@gmail.com}{jhinresh@gmail.com} | \href{https://github.com/JhiNResH}{GitHub} | \href{https://www.linkedin.com/in/chien-jui-jerry-chen-21a11720a/}{LinkedIn}
\end{center}
% Education
\section{Education}
\noindent \textbf{Westcliff University} -- MS in Computer Science \hfill Exp. 2026 \\
\noindent \textbf{University of Texas at Arlington} -- MS in Information Systems \hfill 2024 \\
\noindent \textbf{University of Texas at Arlington} -- MS in Mechanical Engineering \hfill 2023 \\
\noindent \textbf{Yuan Ze University} -- BS in Mechanical Engineering \hfill 2021
% Technical Skills
\section{Technical Skills}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Languages/Frameworks}: TypeScript, Rust, Solidity, Python, React.js, Next.js, Node.js, Anchor
    \item \textbf{Tools/Web3}: Hardhat, Foundry, ZK Circuit, Noir, SQL, TailwindCSS, JQuery, MongoDB, Git,
\end{itemize}
% Experience
\section{Experience}
\entry{Investment Analyst Intern}{Dev 2025 -- Present}{True Phil Venture Capital}{Remote}
\begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Conduct market research and thematic analysis across Web3 emerging frontier tech sectors.
    \item Source high-potential early-stage founders, communities, events, and product-facing analysis.
    \item Draft investment memos, competitive landscape maps, and founder outreach briefs.
    \item Support due diligence by evaluating product traction, token models, business models, and market size.
    \item Assist with portfolio monitoring and follow-up communication with founders.
\end{itemize}

\entry{Founder / CEO}{Aug 2024 -- June 2025}{Sponge (DeFi Startup)}{Remote}
\begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Founded a DeFi startup focused on stablecoin yield optimization; lead a team of 4 engineers.
    \item Architected the full-stack application using Rust (backend) and React/Next.js (frontend).
    \item Designed and deployed smart contracts on Solana.
\end{itemize}
\vspace{1pt}

\entry{Growth Developer Intern}{July 2024 -- Oct 2024}{Perena}{Remote}
\begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Developed responsive frontend interfaces for a stablecoin platform using React and TailwindCSS.
    \item Integrated RESTful APIs to display real-time market data, reducing page load time by 20\%.
\end{itemize}

\entry{Fellowship}{March 2024 -- Nov 2024}{Wormhole}{Remote}
\begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Authored technical research papers on Cross-Chain Interoperability Protocol (CCIP).
    \item Moderated community channels and guide users using cross-chain protocol with Wormhole between Solana and other chains.
\end{itemize}

\entry{Frontend Engineer}{Dec 2023 -- Feb 2024}{Dissect (NFTFI)}{Remote}
\begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Built application webpages using React.js and TailwindCSS.
    \item Collaborated on frontend architecture and component design.
\end{itemize}

\entry{R\&D Intern}{Feb 2020 -- June 2020}{Fortune Electric Co., Ltd.}{Taiwan}
\begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Designed power plant components using AutoCAD and SolidWorks.
    \item Organized and processed customer data into the cloud using Python and Excel.
\end{itemize}

\section{Leadership \& Volunteering}
\entry{Ambassador}{March 2024 -- July 2024}{Accumulated Finance}{Remote}
\begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Authored technical papers on omnichain liquid staking protocols integrated with Curve Finance.
    \item Moderated community channels and guided users on liquid staking strategies.
\end{itemize}
\vspace{2pt}
\entry{Ambassador}{Sep 2024 -- Nov 2024}{Zeus Network}{Remote}
\begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Research and proposed for Defi campaign on Zeus Network.
    \item Moderated community channels and guided users on zBTC and the ecosystem of Zeus Network.
\end{itemize}

\entry{Prepared Angel (Volunteer)}{Oct 2022 -- Nov 2023}{Binance}{Remote}
\begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Maintained Discord community and organized regular events.
    \item Developed Discord bots to automate information retrieval and improve community efficiency.
\end{itemize}
% Projects & Awards
\section{Projects \& Awards}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Uniswap Hook Incubator} (2026): Cohort 8 - Kindred (Uniswap V4/Foundry)
    \item \textbf{Solana Solaris Accelerator} (2025): Cohort 1 - Sponge (Anchor/Rust)
    \item \textbf{Solana Foundation Grants} (2025): USA Grants - Sponge (Anchor/Rust)
    \item \textbf{Jito Grid Hackathon} (2025): 1st Place - Sponge (Anchor/Rust)
    \item \textbf{SOON Genesis Hackathon} (2024): 5th Place - Sponge (Anchor/Rust)
    \item \textbf{Taipei Blockchain Week Hackathon} (2024): 2nd Place (Raydium Defi) - Sponge (Anchor/Rust)
    \item \textbf{Solana Colosseum Breakout Hackathon} (2024): 1st Place (Taiwan), 3rd Place (Chinese \& Solayer AVS) - Sponge
    \item \textbf{XueDao Connect Hackathon} (2024): 3rd Place (Cathay Financial) - Trucritic (Anchor/Rust)
    \item \textbf{EasyA Consensus Hackathon} (2024): Honorable Mention - Stackey (Clarity)
\end{itemize}
\end{document}